Improving Item-Item Similarity Estimation during Collaborative Filtering

### 2014-03-26 paper/paper.tex
Add Conclusion.

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=0.9\textwidth]{MSE_SimR_40.png}
    \includegraphics[width=0.9\textwidth]{MSE_SimR_80.png}
	\caption{Mean square error {\em vs} number of common reviewers, $n$, for
estimates of {\em TrueSimR} for item pairs ultimately having at least 40 common
reviewers (top) and 80 common reviewers (bottom). The dashed curve represents
{\em SimR} computed using only the ratings from the first $n$ reviewers. The
flat red line indicate the MSE that results from always guessing the average
{\em TrueSimR} from the training set. The green curve is {\em LinRegSim} and the
blue curve is {\em UserPredSim}. }
    \label{fig:MSE_SimR}
\end{figure}

@@

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=0.9\textwidth]{MSE_SimP_80.png}
	\caption{Mean square error {\em vs} number of common reviewers, $n$, for
estimates of {\em TrueSimP} for item pairs ultimately having at least 80 common
reviewers. The dashed curve represents {\em CosSim} computed using only the
ratings from the first $n$ reviewers. The flat red line indicate the MSE that
results from always guessing the average {\em TrueSimPref} from the training
set. The green curve is {\em LinRegSim} and the blue curve is {\em UserPredSim}.
}
    \label{fig:MSE_SimP}
\end{figure}

@@

\section*{Conclusion}
\section*{Future Work}
The results achieved over this dataset were significant. In order to show that
the techniques are general, though, we would like to run the same experiments on
other datasets, with different types of items and user behavior. The 
assumptions made for this model were not specific to the data used, so we 
hope to achieve similar results. It would also be interesting to see how 
different the learned parameters would be for other datasets and how well 
the techniques could perform using the same parameters learned here.

>>>>

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=0.9\textwidth]{MSE_SimR_40.png}
    \includegraphics[width=0.9\textwidth]{MSE_SimR_80.png}
	\caption{Mean square error {\em vs} number of common reviewers, $n$, for
estimates of {\em TrueSimRand} for item pairs ultimately having at least 40
common reviewers (top) and 80 common reviewers (bottom). The dashed curve
represents {\em SimR} computed using only the ratings from the first $n$
reviewers. The flat red line indicate the MSE that results from always guessing
the average {\em TrueSimR} from the training set. The green curve is {\em
LinRegSim} and the blue curve is {\em UserPredSim}. }
    \label{fig:MSE_SimR}
\end{figure}

@@

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=0.9\textwidth]{MSE_SimP_80.png}
	\caption{Mean square error {\em vs} number of common reviewers, $n$, for
estimates of {\em TrueSimPref} for item pairs ultimately having at least 80
common reviewers. The dashed curve represents {\em CosSim} computed using only
the ratings from the first $n$ reviewers. The flat red line indicate the MSE
that results from always guessing the average {\em TrueSimPref} from the
training set. The green curve is {\em LinRegSim} and the blue curve is {\em
UserPredSim}.  }
    \label{fig:MSE_SimP}
\end{figure}

@@

\section*{Conclusion}

In this report, we explored the issue of item-item similarity in the context of
collaborative filtering. Estimates of item-item similarity such as the Pearson
correlation and cosine similarity can have very large variances as data is
acquired, yielding large discrepancies between early results and those computed
later after sufficient rating data is acquired. We described an off-line
experiment that simulates the accumulation of rating data over time and the
impact that this data has on the performance of various similarity estimators.
Two new similarity estimators were described and analyzed.

The first is based on a model of noisy score observations. Using a series of
linear regressions, this estimator consistently performs as well or better than
both the Pearson correlation or cosine similarity at estimating future values of
these same functions. The second new estimator is based on a model of noisy
rating pairs generated by an item pair having a true, but unknown, similarity.
This method uses a parametrized surface to efficiently estimate item-item
similarity given only a single pair of ratings. Combining these implied
similarity ``predictions'' with the notion of {\em user predictivity}, we
constructed a novel item-item similarity estimator that performs very well, but
whose effectiveness appears limited to estimations of future Pearson
correlation.

\section*{Future Work}
The results achieved over this dataset were significant. In order to show that
the techniques are general, though, we would like to run the same experiments on
other datasets, with different types of items and user behavior. The 
assumptions made for this model were not specific to the data used, so we 
hope to achieve similar results. It would also be interesting to see how 
different the learned parameters would be for other datasets and how well 
the techniques could perform using the same parameters learned here.
